A Reproducible Data Analysis Workflow with RMarkdown, Git, Make & Docker

### 2019-12-02 manuscript.Rmd
change sha - thanks to Felix Schönbrodt for spotting

```{r}
x <- data.frame(VAR1=c(1,2,3,4),VAR2=c(0,4,6,9) )
checksum <- digest::sha1(x)
if (checksum != "740e88404c04af1d67ffc87b008231c093539cc1"){
  error("Wrong data file loaded or data has been changed!")
}
```

>>>>

```{r}
x <- data.frame(VAR1=c(1,2,3,4),VAR2=c(0,4,6,9) )
checksum <- digest::sha1(x)
if (checksum != "bd4b9197ff7f8e32e56b9d62c3ee7718f367b485"){
  warning("Wrong data file loaded or data has been changed!")
}
```
